Illustrating splines using the Worcester Heart Attack Study

### 2024-08-15 text/04/early-stopping-animal.Rmd

```{}
par(mar=c(4,5,0,0)+0.1,cex=2,pch="+")
f.p <- function(mua) {
  x1 <- rnorm(12)
  x2 <- mua+rnorm(12)
  p.value <- rep(NA,12)
  for (i in 2:12) {
    p.value[i] <- t.test(x1[1:i],x2[1:i])p.value
 }
 plot(p.value,type="b",ylim=0:1,cex=2)
 abline(h=0.05)
}
for (i in 1:100) {
  f.p(mua=1)
}
```

>>>>

```
par(mar=c(4,5,0,0)+0.1,cex=2,pch="+")
f.p <- function(mua) {
  x1 <- rnorm(12)
  x2 <- mua+rnorm(12)
  p.value <- rep(NA,12)
  for (i in 2:12) {
    p.value[i] <- t.test(x1[1:i],x2[1:i])p.value
 }
 plot(p.value,type="b",ylim=0:1,cex=2)
 abline(h=0.05)
}
for (i in 1:100) {
  f.p(mua=1)
}
```

### 2024-08-15 text/14/qqplot.Rmd

---
title: "The qqplot"
author: "Steve Simon"
source: "http://www.pmean.com/qqplot.html"
date: "2014-01-01"
category: 
- Blog post
tags:
- Checking assumptions  
- Linear regression
- R software
- Rmarkdown graphs
output: html_document
page_update: partial
---

>>>>

---
title: "The qqplot"
author: "Steve Simon"
source: "http://www.pmean.com/qqplot.html"
date: "2014-01-01"
categories: 
- Blog post
tags:
- Checking assumptions  
- Linear regression
- R software
- Rmarkdown graphs
output: html_document
page_update: partial
---

### 2024-08-15 text/15/missing-values-in-r.Rmd

---
title: "Missing values in R talk"
author: "Steve Simon"
source: "http://blog.pmean.com/missing-values-in-r/"
date: "2015-02-07"
category:
- Blog post
tags:
- R software
output: html_document
page_update: complete
---

>>>>

---
title: "Missing values in R talk"
author: "Steve Simon"
source: "http://blog.pmean.com/missing-values-in-r/"
date: "2015-02-07"
categories:
- Blog post
tags:
- R software
output: html_document
page_update: complete
---

### 2024-08-15 text/16/circle.Rmd

```{}
draw.circle <- function(x0, y0, r, adjust.units=function() {list(x=1, y=1)}, ...) {
  # draw a circle of radius r centered at x0, y0
  # with an adjustment in the horizontal and vertical dimensions
  # The default adjustment is no adjustment
  pi.seq <- seq(0, 2*pi, length=100)
  adj <- adjust.units()
  x.circle <- x0 + adj$x * r * cos(pi.seq)
  y.circle <- y0 + adj$y * r * sin(pi.seq)
  polygon(x.circle, y.circle, ...)
}

@@

```{}
## The range of the plotting region is 21.6 54 in user coordinates
## The range of the plotting region is 5.759999 3.159999 in inches
## There are 3.75 17.08861 user coordinates per inch
```

```{}
text(15, 25, "r=0.5 (in)")
```

@@

```{}
plot(0, 0, xlim=c(0, 20), ylim=c(0, 50), type="n", xlab=" ", ylab=" ")
co <- c("black", "blue", "red", "green")
points(rep( 5, 4), 10*(1:4), pch=21,  cex=1:4, col=co, bg=rev(co))
points(rep(10, 4), 10*(1:4), pch="o", cex=1:4, col=co)
points(rep(15, 4), 10*(1:4), pch="O", cex=1:4, col=co)
```

>>>>

```
draw.circle <- function(x0, y0, r, adjust.units=function() {list(x=1, y=1)}, ...) {
  # draw a circle of radius r centered at x0, y0
  # with an adjustment in the horizontal and vertical dimensions
  # The default adjustment is no adjustment
  pi.seq <- seq(0, 2*pi, length=100)
  adj <- adjust.units()
  x.circle <- x0 + adj$x * r * cos(pi.seq)
  y.circle <- y0 + adj$y * r * sin(pi.seq)
  polygon(x.circle, y.circle, ...)
}

@@

```
## The range of the plotting region is 21.6 54 in user coordinates
## The range of the plotting region is 5.759999 3.159999 in inches
## There are 3.75 17.08861 user coordinates per inch
```

```
text(15, 25, "r=0.5 (in)")
```

@@

```
plot(0, 0, xlim=c(0, 20), ylim=c(0, 50), type="n", xlab=" ", ylab=" ")
co <- c("black", "blue", "red", "green")
points(rep( 5, 4), 10*(1:4), pch=21,  cex=1:4, col=co, bg=rev(co))
points(rep(10, 4), 10*(1:4), pch="o", cex=1:4, col=co)
points(rep(15, 4), 10*(1:4), pch="O", cex=1:4, col=co)
```

### 2024-08-15 text/21/read-acs-data.Rmd

```{r read-acs-data-01}
library(tidycensus)
library(tidyverse)
library(viridis)
key <- Sys.getenv("CENSUS_API_KEY")
census_api_key("11bafd82737f7d75b3305ada1e772501d0eab002")
tarr <- get_acs(geography = "tract", variables = "B19013_001",
state = "TX", county = "Tarrant", geometry = TRUE)
ggplot(tarr, aes(fill = estimate, color = estimate)) +
geom_sf() +
coord_sf(crs = 26914) +
scale_fill_viridis(option = "magma") +
scale_color_viridis(option = "magma")
```

>>>>

```{r read-acs-data-01}
library(tidycensus)
library(tidyverse)
library(viridis)
key <- Sys.getenv("CENSUS_API_KEY")
census_api_key(key)
tarr <- get_acs(geography = "tract", variables = "B19013_001",
state = "TX", county = "Tarrant", geometry = TRUE)
ggplot(tarr, aes(fill = estimate, color = estimate)) +
geom_sf() +
coord_sf(crs = 26914) +
scale_fill_viridis(option = "magma") +
scale_color_viridis(option = "magma")
```

### 2024-08-15 text/22/analysis-of-means-example.Rmd

---
title: "A simple visual alternative to all pairwise comparisons"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags: 
- Analysis of means
- Rmarkdown graphs
source: new
page_update: complete
---

>>>>

---
title: "A simple visual alternative to all pairwise comparisons"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
categories: Blog post
tags: 
- Analysis of means
- Rmarkdown graphs
source: new
page_update: complete
---

### 2024-08-15 text/22/box-with-no-whiskers.Rmd

---
title: "My boxplot shows a box but no whiskers"
author: "Steve Simon"
date: '2022-12-15'
output:
  html_document: default
category: Blog post
tags:
- Graphical display
source: new
page_update: complete
---

>>>>

---
title: "My boxplot shows a box but no whiskers"
author: "Steve Simon"
date: '2022-12-15'
output:
  html_document: default
categories: Blog post
tags:
- Graphical display
source: new
page_update: complete
---

### 2024-08-15 text/22/different-parameterizations.Rmd

---
title: "Different parameterizations for one factor ANOVA"
author: "Steve Simon"
source: new
date: "2022-07-06"
category: 
- Blog post
tags:
- Analysis of variance
- Rmarkdown code
output: html_document
page_update: complete
---

>>>>

---
title: "Different parameterizations for one factor ANOVA"
author: "Steve Simon"
source: new
date: "2022-07-06"
categories: 
- Blog post
tags:
- Analysis of variance
- Rmarkdown code
output: html_document
page_update: complete
---

### 2024-08-15 text/22/mapping-longitude-latitude.Rmd

---
title: "Mapping latitude and longitude"
author: "Steve Simon"
source: new
date: "2022-01-06"
category: 
- Blog post
tags:
- Geocoding
output: html_document
page_update: complete
---

>>>>

---
title: "Mapping latitude and longitude"
author: "Steve Simon"
source: new
date: "2022-01-06"
categories: 
- Blog post
tags:
- Geocoding
output: html_document
page_update: complete
---

### 2024-08-15 text/24/survival-spline.Rmd

```{r survival-spline-01, echo=FALSE, message=FALSE, warning=FALSE}
library(broom)
library(pspline)
library(readr)
library(rms)
library(tidyverse)
library(yaml)
f0 <- "https://raw.githubusercontent.com/pmean/datasets/master/"
f1 <- "whas100.yaml"
dd <- read_yaml(paste0(f0, f1))
```

>>>>

```{r survival-spline-01, echo=FALSE, message=FALSE, warning=FALSE}
library(broom)
library(pspline)
library(readr)
library(rms)
library(survival)
library(tidyverse)
library(yaml)
f0 <- "https://raw.githubusercontent.com/pmean/datasets/master/"
f1 <- "whas100.yaml"
dd <- read_yaml(paste0(f0, f1))
```
